Results

### 2024-03-04 Analysis/04_Summarise_results.Rmd
Update 04_Summarise_results.Rmd

```{r, echo = FALSE}
## Creating the list of results
all_results_2d <- list(equalizing   = equalizing_2d,
                       facilitation = facilitation_2d,
                       filtering    = filtering_2d,
                       competition  = competition_2d)
all_results_3d <- list(equalizing   = equalizing_3d,
                       facilitation = facilitation_3d,
                       filtering    = filtering_3d,
                       competition  = competition_3d)
empirical_results <- list(combined_empirical)

@@

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 9, width = 9)
fancy.plot(scaled_results_emp, col = col_vector, lm = model_fits_emp, null = null_differences_emp, metric.names = fancy_names)
dev.off()
```

>>>>

```{r, echo = FALSE}
## Creating the list of results
all_results_2d <- list(equalizing   = equalizing_2d,
                       facilitation = facilitation_2d,
                       filtering    = filtering_2d,
                       competition  = competition_2d)
all_results_3d <- list(equalizing   = equalizing_3d,
                       facilitation = facilitation_3d,
                       filtering    = filtering_3d,
                       competition  = competition_3d)
empirical_results <- list(empirical = combined_empirical)

@@

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 9, width = 4)
fancy.plot(scaled_results_emp, col = col_vector, lm = model_fits_emp, null = null_differences_emp, metric.names = rev(fancy_names))
dev.off()
```
